---
title: "Brownlows Bets"
author: "Kristina Larson"
date: "November 11, 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tidyverse)
require(knitr)
```
### `r as.character(Sys.Date())`

```{r}
days=1:365
saveProfit=vector("numeric")
for(run in 1:1000){

  
profit=0
for(i in 1:637){ 
  bdays=sample(days,size=35,replace=TRUE)
  n=length(unique(bdays))
  if(n<35){
    profit=profit+1
  } else{profit=profit-2}
}
saveProfit[run]=profit
}

```
```{r}
hist(saveProfit)
```
```{r}
sortProfit=sort(saveProfit)
print(sortProfit[25])
print(sortProfit[975])
```

The 95% confidence level shows that the values range from `r sortProfit[25]` to `r sortProfit[975]`. However every time you run this code, the range will always change. 


```{r}
days=1:365
saveProfit=vector("numeric")
for(run in 1:1000){

  
profit=0
for(i in 1:637){ 
  bdays=sample(days,size=28,replace=TRUE)
  n=length(unique(bdays))
  if(n<28){
    profit=profit+1
  } else{profit=profit-2}
}
saveProfit[run]=profit
}

```
```{r}
hist(saveProfit)
```



We know that a class size of 35 is too large of a class for a 2:1 ratio. A class size of either 28 or 29 is the right size for Dr J to have a chance of 2:1 or lower of winning this bet. 

```{r}
days=1:365
saveProfit=vector("numeric")
for(run in 1:1000){

  
profit=0
for(i in 1:637){ 
  bdays=sample(days,size=35,replace=TRUE)
  n=length(unique(bdays))
  if(n<35){
    profit=profit+1
  } else{profit=profit-4.75}
}
saveProfit[run]=profit
}

```
```{r}
hist(saveProfit)
```

To make this bet where Dr. J would lose more than 2:1 in the bet, he would have to change the bet to approximately 4.75:1. 



