---
title: "Brownlows Bets"
author: "Kristina Larson"
date: "November 11, 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tidyverse)
require(knitr)
```
### `r as.character(Sys.Date())`

```{r}
days=1:365
saveProfit=vector("numeric")
for(run in 1:1000){

  
profit=0
for(i in 1:637){ 
  bdays=sample(days,size=35,replace=TRUE)
  n=length(unique(bdays))
  if(n<35){
    profit=profit+1
  } else{profit=profit-2}
}
saveProfit[run]=profit
}

```
```{r}
hist(saveProfit)
```
```{r}
sortProfit=sort(saveProfit)
print(sortProfit[25])
print(sortProfit[975])
```

The 95% confidence level shows that the values range from `r sortProfit[25]` to `r sortProfit[975]`. However every time you run this code, the range will always change. 


```{r}
days=1:365
saveProfit=vector("numeric")
for(run in 1:1000){

  
profit=0
for(i in 1:637){ 
  bdays=sample(days,size=28,replace=TRUE)
  n=length(unique(bdays))
  if(n<28){
    profit=profit+1
  } else{profit=profit-2}
}
saveProfit[run]=profit
}

```
```{r}
hist(saveProfit)
```



We know that a class size of 35 is too large of a class for a 2:1 ratio. A class size of either 28 or 29 is the right size for Dr J to have a chance of 2:1 or lower of winning this bet. 

```{r}
days=1:365
saveProfit=vector("numeric")
for(run in 1:1000){

  
profit=0
for(i in 1:637){ 
  bdays=sample(days,size=35,replace=TRUE)
  n=length(unique(bdays))
  if(n<35){
    profit=profit+1
  } else{profit=profit-4.75}
}
saveProfit[run]=profit
}

```
```{r}
hist(saveProfit)
```

To make this bet where Dr. J would lose more than 2:1 in the bet, he would have alter change the bet to approximately 4.75:1. 

<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 637 times so far. Where do you think his profits are? Discuss this in a markdown document

# Methods

<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 637 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->


# Profit Estimate

<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting profits!-->


# Confidence interval of Brownlows earning

<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows winnings (or losings)-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->

